Hector Permafrost

### 2019-06-03 analysis/paper/paper.Rmd
Add parameter draws to paper. Cleanup.

```{r fig-parameter-distribution, fig.cap = param_dist_cap}
param_dist_cap <- paste(
  "Input parameter distributions for global Hector."
)
readd(draws_plot)
```

@@

@@

>>>>

@@

```{r fig-global-dist, fig.cap = global_dist_cap}
global_dist_cap <- paste(
  "Input parameter distributions for global Hector."
)
readd(draws_global_sims)
```

@@

```{r fig-biome-dist, fig.cap = biome_dist_cap, fig.dim = c(9, 9)}
biome_dist_cap <- paste(
  "Input parameter distributions for global Hector."
)
readd(draws_biome_sims)
```
